~\\[1in] % hack to put space at top.
\textbf{\Huge Acknowledgments}\\

It's taken a long time to get to this point, and I truly could not have gotten here without the help and support of  amazing mentors, teachers, colleagues, collaborators, friends, and family.
There are so may people without whom this work would not have been possible, or at least not as enjoyable and productive. ``No man is an island'' could not be more true.

First, thank you to my mentors, Attila Losonczy and Joseph Gogos. They provided the opportunity to do great science and work on fascinating projects. Their guidance helped me progress as a researcher and kept me moving in the right direction, despite the occasional slowdown/interruption. There is no other place I would have rather been for my Ph.D. than Attila's lab. He showed me what it takes to do high quality research, and was supportive and understanding throughout the entire process. Thank you.

I was very fortunate to work with such an amazing group of colleagues in Attila's lab. Collaboration was central to my lab work, and having a group of colleagues who were always willing to help and progress together as a lab, was invaluable.
In particular, Nathan Danielson and Patrick Kaifosh are incredibly brilliant scientists who became great friends. Whether collaborating on projects, developing shared infrastructure, discussing the issue of the moment, or just grabbing lunch, they made every day in lab fun, interesting, and fulfilling. Thank you.
Special thanks to Natasha Diamantopoulou for years of wonderful collaboration on the \df/ project.
To the rest of Attila's lab, thanks for everything: Matthew Lovett-Barron, Gergely Turi, Thomas Reardon, Jack Bowler, Angel Castro, Mohsin Ahmed, Fraser Sparks, Max Ladow, Sebi Rolotti, Wen Li, Elizabeth Balough, Ali Kaufman, Joseph Tsai, Adrian Negrean, Andres Grosmark, Rita Nylias. and Jeff Zhang.

Thank you to my parents, grandparents, and brother for all of the support through the years that helped me get here. Most important of all, this truly would not have been possible without the continuous support of my wife, Kate. Through the late nights working together and the long weeks working apart, the past few years have been a bit crazy. Thank you for always being there and understanding all the ups and downs. Finally, Rose, born somewhere in the middle of \autoref{ch:df}, thanks for being the best baby to ever baby.
\\

Thank you to the National Institute of Mental Health for pre-doctoral fellowship support: NIMH 1F31MH105169-01A1.

